\section*{\centering ACKNOWLEDGEMENTS}\addcontentsline{toc}{section}{ACKNOWLEDGEMENTS}
\hspace{1.27cm}
First and foremost, I would like to express my deepest gratitude to my thesis advisor, \textbf{Asst.\ Prof.\ Dr.\ SRANG Sarot}, Head of ECAM-LaSalle Phnom Penh and the Dynamics and Control Laboratory, and \textbf{Mr.\ SREY Sokserey}, for their invaluable guidance, continuous support, and encouragement throughout the course of this research. Their expertise and dedication to providing constructive feedback, despite their demanding schedules, have been instrumental in shaping this work and guiding it to completion.

\par
\hspace{1.27cm}
I would also like to extend my sincere appreciation to \textbf{H.E.\ Prof.\ Dr.\ PO Kimtho}, the Director of the Institute of Technology of Cambodia, and \textbf{Dr.\ CHAN Sarin}, the Head of the Department of Industrial Engineering and Mechanical Engineering, for their exceptional leadership and for providing an excellent academic environment and the necessary resources to carry out this research.
\par
\hspace{1.27cm}
My heartfelt thanks go to all the faculty members and staff of the Department of Industrial Engineering and Mechanical Engineering at the Institute of Technology of Cambodia for their academic support and inspiration throughout my studies.
\par
\hspace{1.27cm}
I am also deeply grateful to my colleagues at ECAM-LaSalle Phnom Penh and the Dynamics and Control Laboratory (DCLab) for their constant assistance and guidance, particularly during the hands-on phases of this project involving fabrication, machining, and system integration. Their willingness to share knowledge and help overcome technical obstacles proved vital to the success of this work.
\par
\hspace{1.27cm}
I am deeply grateful to my family for their unconditional love, sacrifice, and encouragement. Their unwavering belief in me has been my greatest source of motivation from the beginning to the end of my studies. Their support and generosity have made this journey possible.
\par
\hspace{1.27cm}
Finally, I wish to thank my friends and colleagues for their assistance, discussions, and moral support during the development of this project.