\printnomenclature
%% This will add the subgroups
%----------------------------------------------
\renewcommand\nomgroup[1]{%
  \item[\bfseries
  \ifstrequal{#1}{A}{%
  \ifstrequal{#1}{B}{%
}}%
]}
%----------------------------------------------
\mbox{}

%___________ ABBREVIATIONS ________________
\nomenclature[A]{\textbf{DOF}}{Degree of Freedom.}
\nomenclature[A]{\textbf{DC}}{Direct Current.}
\nomenclature[A]{\textbf{ROS\,2}}{Robot Operating System 2.}
\nomenclature[A]{\textbf{PC}}{Personal Computer.}
\nomenclature[A]{\textbf{CAD}}{Computer Aided Design.}
\nomenclature[A]{\textbf{2D}}{Two Dimensional.}
\nomenclature[A]{\textbf{3D}}{Three Dimensional.}
\nomenclature[A]{\textbf{FK}}{Forward Kinematics.}
\nomenclature[A]{\textbf{IK}}{Inverse Kinematics.}
\nomenclature[A]{\textbf{BLDC}}{Brushless DC Motor.}
\nomenclature[A]{\textbf{FOC}}{Field Oriented Control.}
\nomenclature[A]{\textbf{CAN}}{Controller Area Network.}
\nomenclature[A]{\textbf{RPM}}{Revolutions per Minute.}
\nomenclature[A]{\textbf{EE}}{End-Effector.}
\nomenclature[A]{\textbf{FSM}}{Finite State Machine.}
\nomenclature[A]{\textbf{YOLO}}{You Only Look Once (object detection algorithm).}
\nomenclature[A]{\textbf{RGB-D}}{Red-Green-Blue and Depth image.}
\nomenclature[A]{\textbf{HSV}}{Hue-Saturation-Value colour space.}
\nomenclature[A]{\textbf{FPS}}{Frames Per Second.}
\nomenclature[A]{\textbf{QDD}}{Quasi-Direct-Drive actuator.}
\nomenclature[A]{\textbf{PP mode}}{Position-Profile control mode.}

%%____________ SYMBOLS ____________
\nomenclature[B]{$v$}{Velocity (\(m/s\)).}
\nomenclature[B]{$\omega$}{Angular Velocity (\(rad/s\)).}
\nomenclature[B]{$T$}{Torque (\(N \cdot m\)).}
\nomenclature[B]{$F$}{Force (\(N\)).}
\nomenclature[B]{$r$}{Radius (\(m\)).}
\nomenclature[B]{$r_f$}{Length of Upper Arm Link (\(m\)).}
\nomenclature[B]{$r_e$}{Length of Lower Arm Link (\(m\)).}
\nomenclature[B]{$e$}{Side Length of Moving Platform Triangle (\(m\)).}
\nomenclature[B]{$f$}{Side Length of Fixed Base Triangle (\(m\)).}
\nomenclature[B]{$\theta_i$}{Joint Angle of $i$-th Arm (\(rad\)).}
\nomenclature[B]{$(x,y,z)$}{Cartesian Position of End-Effector (\(mm\)).}
\nomenclature[B]{$(u,v)$}{Pixel Coordinates in Image Frame (\(px\)).}
\nomenclature[B]{$f_x, f_y$}{Camera Focal Lengths in $x$ and $y$ (\(px\)).}
\nomenclature[B]{$c_x, c_y$}{Camera Principal Point Coordinates (\(px\)).}
\nomenclature[B]{$Z$}{Depth from Camera to Object (\(mm\)).}
\nomenclature[B]{$\mathbf{R}$}{Rotation Matrix of Camera-to-Robot Transform.}
\nomenclature[B]{$\mathbf{t}$}{Translation Vector of Camera-to-Robot Transform (\(mm\)).}
\nomenclature[B]{$v_y$}{Conveyor Belt Velocity in $Y$ direction (\(mm/s\)).}
\nomenclature[B]{$t_{\text{total}}$}{Total Prediction Delay (\(s\)).}
\nomenclature[B]{$a_{\max}$}{Maximum End-Effector Acceleration (\(mm/s^2\)).}
\nomenclature[B]{$v_{\max}$}{Maximum End-Effector Velocity (\(mm/s\)).}
\nomenclature[B]{$K$}{EE Correction Proportional Gain (dimensionless).}
\nomenclature[B]{$J$}{Jacobian Matrix.}
\nomenclature[B]{$g$}{Gravitational Acceleration (\(m/s^2\)).}
